### 2021-11-14 sections/strategy_Htautau.tex
modify some plots

The final observable used to extract signal events is defined as the BDT distribution in each SRs corresponding to either $tuH$ or $tcH$ signal.
Figure~\ref{fig:asimov_prefitbdt} show the prefits to the data of BDT observable in each SRs with all background processes
constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l2tau1bnj_os/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(a1)}}
%\put(-30, 80){\textbf{(a1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(a2)}}
%\put(-30, 80){\textbf{(a2)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(a3)}} 
%\put(-70, 70){\textbf{(a3)}}
\\
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(b1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b3j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(b2)}}\\
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(c1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(c2)}}\\
\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
  $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2). Only statistical uncertainties are being shown (?). Underflow and overflow bins are included
respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau
contributions shown from $t\bar{t}$, Ztautau and other MC including diboson, single top, and V+jets.}
\label{fig:taupt_postfit}
\end{figure}

%\input{\FCNCFigures/tex/BDT}
\begin{figure}[H]
\centering
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l2tau1bnj_os/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(a1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b1j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(a2)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(a3)}}\\
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(b1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b3j_os_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(b2)}}\\
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(c1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(c2)}}\\
\caption{ The BDT output distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
  $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2). Only statistical uncertainties are being shown (?). Underflow and overflow bins are included
respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau
contributions shown from $t\bar{t}$ and other MC including diboson, single top, and V+jets.}
\label{fig:asimov_prefitbdt}
\end{figure}

>>>>

The final observable used to extract signal events is defined as the BDT distribution in each SRs corresponding to either $tuH$ or $tcH$ signal.
Figure~\ref{fig:asimov_prefitbdt} show the prefits to the data of BDT observable in each SRs with all background processes
constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(a1)}}
%\put(-30, 80){\textbf{(a1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(a2)}}
%\put(-30, 80){\textbf{(a2)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(a3)}} 
%\put(-70, 70){\textbf{(a3)}}
\\
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(b1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b3j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(b2)}}\\
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(c1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(c2)}}\\
\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
  $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2). Only statistical uncertainties are being shown (?). Underflow and overflow bins are included
respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau
contributions shown from $t\bar{t}$, Ztautau and other MC including diboson, single top, and V+jets.}
\label{fig:taupt_postfit}
\end{figure}

%\input{\FCNCFigures/tex/BDT}
\begin{figure}[H]
\centering
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(a1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(a2)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(a3)}}\\
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(b1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b3j_os_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(b2)}}\\
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(c1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(c2)}}\\
\caption{ The BDT output distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
  $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2). Only statistical uncertainties are being shown (?). Underflow and overflow bins are included
respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau
contributions shown from $t\bar{t}$ and other MC including diboson, single top, and V+jets.}
\label{fig:asimov_prefitbdt}
\end{figure}
